---
title: "Covid_Population_density"
author: "James Wilson"
date: "11/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Population Density Graph

``` {r}
#**This data uses just population, NOT population density**

Population_Density<- read.csv("/Users/jameswilson/desktop/Bio290/Final_Project/Population_Density.csv")

#Population_Density<- Population_Density %>% 
  #rename(
   # Density_km= density
  #)


#Exponential_2 <- Population_Density[ which(Population_Density$country== c('Australia', 'Canada', 'Croatia', 'Israel', 'New_Zealand', 'North_Macedonia', 'Oman', 'United_Arab_Emirates', 'United_States')), ]

#Real Data
Exponential <- Population_Density[Population_Density $countriesAndTerritories %in% c('Australia', 'Canada', 'Croatia', 'Israel', 'New_Zealand', 'North_Macedonia', 'Oman', 'United_Arab_Emirates', 'United_States', "Austria", "Dominican_Republic","Ecuador", "Ireland", "Lithuania", "Malaysia", "Portugal", "South Africa", "United_Kingdom", "Georgia", "Italy", "Bosnia_and_Herzegovina", "Chile", "Costa_Rica", "Czech_Republic", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Latvia", "Lebanon", "Panama", "Poland", "Romania", "Saudi_Arabia", "Serbia", "Singapore", "Spain", "Switzerland", "Trinidad_and_Tobago"), ]

Power_Law <-Population_Density[Population_Density $countriesAndTerritories %in% c("Albania", "Armenia", "Belgium", "Cyprus", "Denmark", "Iran", "Jordan", "Mauritius", "Moldova", "Netherlands", "Norway", "Qatar", "Slovakia", "Sweden", "Turkey", "Uruguay", "Bahrain", "Bulgaria", "Kuwait"), ] 

model_fits_Rsquared[ ,1]
```


Exponential: 'Australia', 'Canada', 'Croatia', 'Israel', 'New_Zealand', 'North_Macedonia', 'Oman', 'United_Arab_Emirates', 'United_States', "Austria", "Dominican_Republic","Ecuador", "Ireland", "Lithuania", "Malaysia", "Portugal", "South Africa", "United_Kingdom", "Georgia", "Italy", "Bosnia_and_Herzegovina", "Chile", "Costa_Rica", "Czech_Republic", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Latvia", "Lebanon", "Panama", "Poland", "Romania", "Saudi_Arabia", "Serbia", "Singapore", "Spain", "Switzerland", "Trinidad_and_Tobago"

Powe_Law: "Albania", "Armenia", "Belgium", "Cyprus", "Denmark", "Iran", "Jordan", "Mauritius", "Moldova", "Netherlands", "Norway", "Qatar", "Slovakia", "Sweden", "Turkey", "Uruguay", "Bahrain", "Bulgaria", "Kuwait"


```{r}
library(tidyverse)

Population_Density_2<- read.csv("/Users/jameswilson/desktop/Bio290/Final_Project/Population_Density_2.csv")

Population_Density_2<- Population_Density_2 %>% 
  rename(
    Density_km= density
  )

Exponential_Density <- Population_Density_2[Population_Density_2 $country %in% c('Australia', 'Canada', 'Croatia', 'Israel', 'New_Zealand', 'North_Macedonia', 'Oman', 'United_Arab_Emirates', 'United_States', "Austria", "Dominican_Republic","Ecuador", "Ireland", "Lithuania", "Malaysia", "Portugal", "South Africa", "United_Kingdom", "Georgia", "Italy", "Bosnia_and_Herzegovina", "Chile", "Costa_Rica", "Czech_Republic", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Latvia", "Lebanon", "Panama", "Poland", "Romania", "Saudi_Arabia", "Serbia", "Singapore", "Spain", "Switzerland", "Trinidad_and_Tobago"), ]


Power_Law_Density <-Population_Density_2[Population_Density_2 $country %in% c("Albania", "Armenia", "Belgium", "Cyprus", "Denmark", "Iran", "Jordan", "Mauritius", "Moldova", "Netherlands", "Norway", "Qatar", "Slovakia", "Sweden", "Turkey", "Uruguay", "Bahrain", "Bulgaria", "Kuwait"), ] 

```


```{r}
#Exponential Data Distribution
density_Ex <- Exponential_Density$Density_km
range(density_Ex)
#Range is 3.3-8239, I used a range from 2-655 (excluding singapore)
breaks_Ex <- seq(3.3, 8239, by=1029)
breaks_Ex
density_Ex.cut <- cut(density_Ex, breaks_Ex, right=FALSE)
density_Ex.freq = table(density_Ex.cut)
density_Ex.freq

#Exponential Actual Distibution
subset(Exponential_Density, Density_km <= 81) #19
subset(Exponential_Density, Density_km <= 163) #11 (30)
subset(Exponential_Density, Density_km <= 245) #4 (34)
subset(Exponential_Density, Density_km <= 327) #2 (36)
subset(Exponential_Density, Density_km <= 409) #0 (36)
subset(Exponential_Density, Density_km <= 491) #1 (37)
subset(Exponential_Density, Density_km <= 573) #0 (37)
subset(Exponential_Density, Density_km <= 655) #1 (38)
subset(Exponential_Density, Density_km <= 9000) #1 (39)


#Power Law Range 
density_Pw <- Power_Law_Density$Density_km
range(density_Pw)
#Range is 16-2224, but exclusde Baharin, use the range 16-623

#Power Law Distributions
subset(Power_Law_Density, Density_km <= 78) #5 (5)
subset(Power_Law_Density, Density_km <= 157) #8 (13)
subset(Power_Law_Density, Density_km <= 236) #0 (13)
subset(Power_Law_Density, Density_km <= 315) #2 (15)
subset(Power_Law_Density, Density_km <= 394) #1 (16)
subset(Power_Law_Density, Density_km <= 476) #1 (17)
subset(Power_Law_Density, Density_km <= 552) #0 (17)
subset(Power_Law_Density, Density_km <= 631) #1 (18)
subset(Power_Law_Density, Density_km <= 3000) #1 (19)
```



```{r}
#Stats for density 

print (mean(Exponential_Density[["Density_km"]]))
print (sd(Exponential_Density[["Density_km"]]))

print (mean(Power_Law_Density[["Density_km"]]))
print (sd(Power_Law_Density[["Density_km"]]))
```

```{r}
 
#Function for overlayed histogram
#ggplot(dat, aes(x=rating, fill=cond)) +
    #geom_histogram(binwidth=.5, alpha=.5, position="identity")

#Graph for Density
Covid_Density_Distribution <- read.csv("/Users/jameswilson/desktop/Bio290/Final_Project/Covid_Density_Distribution.csv")

ggplot(Covid_Density_Distribution,aes(x=Population_Density_km2,y=Probability_Distribution,fill=Condition)) + 
        geom_bar(stat="identity",position = "identity", alpha=.2)+ theme_minimal() +scale_fill_manual(values=c("#E69F00", "#56B4E9")) + ggtitle("Probability Distribution of Population Density")


        #Failed Attempts
#ggplot(Covid_Density_Distribution, aes(x = Proportion, fill = Condition)) +   # Draw overlaying histogram
  #geom_histogram(position = "identity", alpha = 0.2, bins = 9)

#Failed Attempts
#ggplot(data=Covid_Density_Distribution, aes(Covid_Density_Distribution$Frequency)) + 
  #geom_histogram()

#ggplot(Covid_Density_Distribution, aes(X, fill = Condition)) +
 # geom_histogram(position = "Proportion", alpha = 0.2, bins = 9)

ggplot(Covid_Density_Distribution,aes(x=X,y=Proportion,fill=Condition)) + 
        geom_bar(stat="identity",position = "identity", alpha=.3)
```

```{r}
#Statistics Test
Ex_Density <- Exponential_Density[,3]
print(Ex_Density)
Pl_Density <- Power_Law_Density[,3]
res <- t.test(Ex_Density, Pl_Density, var.equal = TRUE)
print

wilcox.test(Ex_Density, Pl_Density, alternative = "two.sided")
```

res[["p.value"]]
[1] 0.8690356

28
56
84
112
140
168
196
224 


49
98
147
196
245
294
343
392
```{r}
#Exponential Population Density Without Outliars
wo_Out_Density_Ex <- Exponential_Density
outlierKD(wo_Out_Density_Ex, Density_km)
wo_Out_Density_Ex$Density_km
#Range is from 3.3-234

#Exponential Density Actual Frequency Distribution
subset(wo_Out_Density_Ex, Density_km <= 28) #7 
subset(wo_Out_Density_Ex, Density_km <= 56) #11 (4)
subset(wo_Out_Density_Ex, Density_km <= 84) #19 (8)
subset(wo_Out_Density_Ex, Density_km <= 112) #26 (7)
subset(wo_Out_Density_Ex, Density_km <= 140) #30 (4)
subset(wo_Out_Density_Ex, Density_km <= 168) #30 (0)
subset(wo_Out_Density_Ex, Density_km <= 196) #30 (0)
subset(wo_Out_Density_Ex, Density_km <= 224) #33 (3)
subset(wo_Out_Density_Ex, Density_km <= 5000) #34 (1)

#Power Population Density Without Outliars
wo_Out_Density_Pw <- Power_Law_Density
outlierKD(wo_Out_Density_Pw, Density_km)
wo_Out_Density_Pw$Density_km
#Range is from 16-409

#Power Law Density Frequency Distribution
subset(wo_Out_Density_Pw, Density_km <= 49) #3 
subset(wo_Out_Density_Pw, Density_km <= 98) #5 (2)
subset(wo_Out_Density_Pw, Density_km <= 147) #13 (8)
subset(wo_Out_Density_Pw, Density_km <= 196) #13 (0)
subset(wo_Out_Density_Pw, Density_km <= 245) #14 (1)
subset(wo_Out_Density_Pw, Density_km <= 294) #15 (1)
subset(wo_Out_Density_Pw, Density_km <= 343) #15 (0)
subset(wo_Out_Density_Pw, Density_km <= 392) #16 (1)
subset(wo_Out_Density_Pw, Density_km <= 10000) #17 (1)

#Graph For Data Without Outliars

Wo_Out_Density_Distribution <- read.csv("/Users/jameswilson/desktop/Bio290/Final_Project/Covid_Density_Outliars.csv")

ggplot(Wo_Out_Density_Distribution,aes(x=Population_Density_km2,y=Probability_Distribution,fill=Condition)) + 
        geom_bar(stat="identity",position = "identity", alpha=.2)+ theme_minimal() +scale_fill_manual(values=c("#E69F00", "#56B4E9")) + ggtitle("Probability Distribution of Population Density")

#Statistics for Density  
O_Ex_Density <- wo_Out_Density_Ex[,3]
print(Ex_Area)
O_Pl_Density <- wo_Out_Density_Pw[,3]

wilcox.test(O_Ex_Density, O_Pl_Density, alternative = "two.sided")

```
68870
137740
206610
275480
344350
413220
482090
550960 
```{r}
#Area Data and Graph

#Exponential Data Distribution
Area_Ex <- Exponential_Density$area
range(Area_Ex)
#range is from 710-9,984,670
wo_Outliar_Exponential <- Exponential_Density


source("http://goo.gl/UUyEzD")
outlierKD(wo_Outliar_Exponential, area)


#Exponential Data Distribution
Area_Ex <- wo_Outliar_Exponential$area
range(Area_Ex)
#range is from 710- 551,695

#Exponential Actual Distibution
subset(wo_Outliar_Exponential, area <= 68870) #12
subset(wo_Outliar_Exponential, area <= 137740) #22 (10)
subset(wo_Outliar_Exponential, area <= 206610) #22 (0)
subset(wo_Outliar_Exponential, area <= 275480) #25 (3)
subset(wo_Outliar_Exponential, area <= 344350) #31 (6)
subset(wo_Outliar_Exponential, area <= 413220) #32 (1)
subset(wo_Outliar_Exponential, area <= 482090) #32 (0)
subset(wo_Outliar_Exponential, area <= 550960) #33 (1)
subset(wo_Outliar_Exponential, area >= 550960) #34 (1)
```

40378
80756
121134
161512
201890
242268
282646
323024
```{r}
#Power Law Area Data Distribution
wo_Outliar_Power <- Power_Law_Density
source("http://goo.gl/UUyEzD")
outlierKD(wo_Outliar_Power, area)

#Range of Data
Area_Pw <- wo_Outliar_Power$area
range(Area_Pw)
Area_Pw
  #range is from 765 - 323,802

#Power Law Actual Frequency Distribution
subset(wo_Outliar_Power, area <= 40378) #9 
subset(wo_Outliar_Power, area <= 80756) #12 (3)
subset(wo_Outliar_Power, area <= 121134) #14 (2) 
subset(wo_Outliar_Power, area <= 161512) #14 (0) 
subset(wo_Outliar_Power, area <= 201890) #15 (1)
subset(wo_Outliar_Power, area <= 242268) #15 (0) 
subset(wo_Outliar_Power, area <= 282646) #15 (0)
subset(wo_Outliar_Power, area <= 323024) #15 (0) 
subset(wo_Outliar_Power, area >= 323024) #16 (1)

#Graph
Covid_Area_Distribution <- read.csv("/Users/jameswilson/desktop/Bio290/Final_Project/Area_Distribution.csv")

ggplot(Covid_Area_Distribution,aes(x=Area_in_km2,y=Probability_Distribution,fill=Condition)) + 
        geom_bar(stat="identity",position = "identity", alpha=.2)+ theme_minimal() +scale_fill_manual(values=c("#E69F00", "#56B4E9")) + ggtitle("Probability Distribution of Area in km^2")

#Mean
mean(wo_Outliar_Exponential[["area"]])
```




```{r}
#Statistics for Area 
Ex_Area <- wo_Outliar_Exponential[,6]
print(Ex_Area)
Pl_Area <- wo_Outliar_Power[,6]

wilcox.test(Ex_Area, Pl_Area, alternative = "two.sided")

#With Outliars

```

``` {r}
#Fixes to Graphs

#Density need to Fix Exponential
subset(wo_Out_Density_Ex, Density_km <= 49) #11 
subset(wo_Out_Density_Ex, Density_km <= 98) #21 (10)
subset(wo_Out_Density_Ex, Density_km <= 147) #30 (9)
subset(wo_Out_Density_Ex, Density_km <= 196) #30 (0)
subset(wo_Out_Density_Ex, Density_km <= 245) #34 (4)
subset(wo_Out_Density_Ex, Density_km <= 294) #34 (0)
subset(wo_Out_Density_Ex, Density_km <= 343) #34 (0)
subset(wo_Out_Density_Ex, Density_km <= 392) #34 (0)
subset(wo_Out_Density_Ex, Density_km <= 10000) #34 (0)

#For area need to Fix Power Law
subset(wo_Outliar_Power, area <= 68870) #12
subset(wo_Outliar_Power, area <= 137740) #14 (2)
subset(wo_Outliar_Power, area <= 206610) #15 (1)
subset(wo_Outliar_Power, area <= 275480) #15 (0)
subset(wo_Outliar_Power, area <= 344350) #16 (1)
subset(wo_Outliar_Power, area <= 413220) #16 (0)
subset(wo_Outliar_Power, area <= 482090) #16 (0)
subset(wo_Outliar_Power, area <= 550960) #16 (0)
subset(wo_Outliar_Power, area >= 550960) #16 (0)
```